A Gentle Introduction into Structural Causal Models

### 2021-05-02 intro.Rmd
hierachy of causation

@@

The rest of the paper is structured as follows: 
The subsequent section examines central assumptions in causal modelling. 
The second section looks at the difference SCMs and BCNs.
The section thereafter studies the hierachy of causation, looking at the different queries in the SCM and the BCN.

>>>>

 |Method          | Action |  Example
|-----------------|---------------------------|------------------------|
| Prediction      | Observation/Co-occurrence | What happened...
| Intervention    | Do-manipulation           | What happens if ...
| Counterfactual  | Hypothetical Realities    | What would have happened if...

@@

The rest of the paper is structured as follows: 
The subsequent section examines central assumptions in causal modelling. 
The section thereafter studies the hierachy of causation, looking at the different queries in the SCM and the BCN.
